Model Comparison

### 2020-02-11 stats/model_comparison.Rmd
update model comparison example

# load model predicitons
test_prag <- readRDS("../saves/test_prag.rds")
test_global <- readRDS("../saves/test_global.rds")
test_flat <- readRDS("../saves/test_flat.rds")

# join predictions with the data

bind_rows(

  test_prag %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct),

  test_global %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct),

   test_flat %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct)
)%>%
  mutate(log_like = log(ifelse(correct == 1, pred, 1 - pred)))%>% # calculate log likelihood
  select(-pred, - correct)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
         prag_vs_flat= pragmatic - flat,
         global_vs_flat = global - flat) %>%
  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
            prag_vs_flat = sum(prag_vs_flat),
            global_vs_flat = sum(global_vs_flat))%>%
  gather(model, logBF)

>>>>

# load model predicitons
test_prag <- readRDS("../saves/test_prag.rds")

test_global <- readRDS("../saves/test_global.rds")

test_flat <- readRDS("../saves/test_flat.rds")

bind_rows(
  test_prag, 
  test_global, 
  test_flat
)%>%
  spread(model, pred)%>%
  right_join(d_model_comp)%>%
  mutate(log_like_prag = log(ifelse(correct == 1, pragmatic, 1 - pragmatic)),
         log_like_global = log(ifelse(correct == 1, global, 1 - global)),
         log_like_flat = log(ifelse(correct == 1, flat, 1 - flat)))%>%
  mutate(prag_vs_global = log_like_prag - log_like_global, # subtract likelihood for each predictions and model
         prag_vs_flat= log_like_prag - log_like_flat,
         global_vs_flat = log_like_global - log_like_flat) %>%
  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
            prag_vs_flat = sum(prag_vs_flat),
            global_vs_flat = sum(global_vs_flat))%>%
  gather(model, logBF)
